Tensor denoising and completion based on ordinal observations

### 2020-03-05 paper/arxiv/correction.tex
update correction

{ \color{red}Correction of~\eqref{eq:clt}. Define the subspace:
\[
\tS=\{\Vec(\tZ): \tZ=-\Theta\otimes \mathbf{1}+\tJ\otimes \mb,\ (\Theta,\mb)\in(\tP,\tB)\}.
\]
We show that Hession is definite negative restricted in the subspace $\tS$. Specifically, for any vector $\mz=\entry{z_{\omega,\ell}}\in\tS$,
\begin{align}
\sum_{\omega,\ell} z^2_{\omega,\ell}\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}&=\sum_{\omega,\ell}(-\theta_\omega+b_\ell)^2\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}\\
&=\sum_{\omega,\ell}(\theta^2_\omega-2\theta_\omega b_\ell + b^2_\ell)\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}\\
&=\sum_{\omega,\ell}\theta^2_\omega\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}-2\sum_{\omega,\ell} \theta_\omega b_\ell \mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}+\sum_{\omega,\ell}b^2_\ell\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}\\
&\geq \sum_{\omega}\theta^2_\omega -2\sum_{\omega,\ell}\theta_\omega b_\ell+\sum_{\ell}b_\ell^2\left(n_{\ell}+n_{\ell+1}\right)\\
&\geq \sum_{\omega}\theta^2_\omega+\min_\ell\left(n_{\ell}+n_{\ell+1}\right)\sum_{\ell}b_\ell^2
\end{align}

@@

Therefore, there exists a positive constant $c_1>0$ (? perhaps depending on $\alpha, \beta,\Delta$ etc...needs some caculation..) such that
\[
\max_{\mz\in\tS,\mz\neq \mathbf{0}}{\sum_{\omega,\ell} z^2_{\omega,\ell}\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}} \over \FnormSize{}{\mz}^2}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}.
\]
The conclusion follows by noting that the ratio ${\min_{\ell}(n_\ell+n_{\ell+1})\over \prod_k d_k} \geq c'A_{\alpha,\beta,\Delta}$ in high probability. 
}

\end{enumerate}1
\end{proof}
\bibliography{tensor_wang}
\bibliographystyle{apalike}
\end{document}

>>>>

{ \color{red}Correction of~\eqref{eq:clt}. Define the subspace:
\[
\tS=\{\Vec(\tZ): \tZ=-\Theta\otimes \mathbf{1}+\tJ\otimes \mb,\ (\Theta,\mb)\in(\tP,\tB)\}.
\]
It suffices to prove the negative definiteness of Hession when restricted in the subspace $\tS$. Specifically, for any vector $\mz=\entry{z_{\omega,\ell}}\in\tS$,
\begin{align}
\sum_{\omega,\ell} z^2_{\omega,\ell}\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}&=\sum_{\omega,\ell}(-\theta_\omega+b_\ell)^2\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}\\
&=\sum_{\omega,\ell}(\theta^2_\omega-2\theta_\omega b_\ell + b^2_\ell)\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}\\
&=\sum_{\omega,\ell}\theta^2_\omega\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}-2\sum_{\omega,\ell} \theta_\omega b_\ell \mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}+\sum_{\omega,\ell}b^2_\ell\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}}\\
&\geq \sum_{\omega}\theta^2_\omega -2\sum_{\omega,\ell}\theta_\omega b_\ell+\sum_{\ell}b_\ell^2\left(n_{\ell}+n_{\ell+1}\right)\\
&\geq \sum_{\omega}\theta^2_\omega+\min_\ell\left(n_{\ell}+n_{\ell+1}\right)\sum_{\ell}b_\ell^2
\end{align}

@@

Therefore, there exists a positive constant $c_1>0$ (? perhaps depending on $\alpha, \beta,\Delta$ etc...needs some calculation..) such that
\[
\max_{\mz\in\tS,\mz\neq \mathbf{0}}{\sum_{\omega,\ell} z^2_{\omega,\ell}\mathds{1}_{\{y_\omega=\ell \text{ or }\ell+1\}} \over \FnormSize{}{\mz}^2}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}\geq c_1 {\min_{\ell}(n_\ell+n_{\ell+1})\over (L-1)\prod_k d_k}. 
\]
The conclusion~\eqref{eq:clt} then follows by applying the law of large number and the uniform bound $\min_{z_{\omega,\ell}}\mathbb{P}(y_{\omega}=\ell \text{ or }\ell+1|z_{\omega,\ell})\geq 2A_{\alpha,\beta,\Delta}$ to the ratio:
\[
{\min_{\ell}(n_\ell+n_{\ell+1})\over \prod_k d_k}\geq 2A_{\alpha,\beta,\Delta}, \quad \text{ in high probability as $d_{\min}\to \infty$}.
\] 
}
\end{enumerate}1
\end{proof}
\bibliography{tensor_wang}
\bibliographystyle{apalike}
\end{document}
